Presentation Title

### 2017-08-13 paper/s1-intro.tex
Spell check paper

% problem description
Bitcoin is almost 10 years old and its market capitalisation is over \$60 billion USD and growing~\cite{bitcoinmarketcap}.
We can be reasonably sure that cryptocurrencies,
even if their application is still somewhat limited,
are here to stay in the foreseeable future.
Driven by the success of Bitcoin, we are seeing a renaissance of consensus research~\cite{miller2016honey, kogias2016enhancing, kokoris2017omniledger},
where the primary focus is to improve the scalability of blockchain system.
This is due to the inefficiencies in the consensus mechanism in early blockchain systems---proof-of-work (PoW).
For example, Bitcoin can only do 7 transactions per second (TPS) at most~\cite{vukolic2015quest}.
While adjusting the block size (which Bitcoin has recently done via SegWit~\cite{segwit}) and/or the block interval may increase TPS,
it also leads to centralisation as larger blocks take longer to propagate in the network,
giving miners that do not have a fast network a disadvantage~\cite{croman2016scaling}.
In today's network, it is not possible to achieve more than 758 TPS
if new blocks need to be propogated timely to 90\% of the network~\cite{croman2016scaling}.

@@

% research question
In this work, answer the following research question.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault-tolerant and horizontally scalable?}
\end{displayquote}
A blockchain consensus protocol should be application neutural,
for example PoW without the transaction logic.
Our system should be Byzantine fault tolerant up to some threshold.
The threshold may be made adjustable by trading off performance.
Finally, we are interested in horizontal scalability in the general case, as it enables ubiquitous use.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.

>>>>

% problem description
Bitcoin is almost 10 years old and its market capitalisation is over \$60 billion USD and growing~\cite{bitcoinmarketcap}.
We can be reasonably sure that cryptocurrencies,
even if their application is still somewhat limited,
are here to stay in the foreseeable future.
Driven by the success of Bitcoin, we are seeing a renaissance of consensus research~\cite{miller2016honey, kogias2016enhancing, kokoris2017omniledger},
where the primary focus is to improve the scalability of blockchain system.
This is due to the inefficiencies in the consensus mechanism in early blockchain systems---proof-of-work (PoW).
For example, Bitcoin can only do 7 transactions per second (TPS) at most~\cite{vukolic2015quest}.
While adjusting the block size (which Bitcoin has recently done via SegWit~\cite{segwit}) and/or the block interval may increase TPS,
it also leads to centralisation as larger blocks take longer to propagate in the network,
giving miners that do not have a fast network a disadvantage~\cite{croman2016scaling}.
In today's network, it is not possible to achieve more than 758 TPS
if new blocks need to be propagated timely to 90\% of the network~\cite{croman2016scaling}.

@@

% research question
In this work, answer the following research question.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault-tolerant and horizontally scalable?}
\end{displayquote}
A blockchain consensus protocol should be application neutral,
for example PoW without the transaction logic.
Our system should be Byzantine fault tolerant up to some threshold.
The threshold may be made adjustable by trading off performance.
Finally, we are interested in horizontal scalability in the general case, as it enables ubiquitous use.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.

### 2017-08-13 paper/s2-problem.tex
Spell check paper

Note that the agreement and validity property are similar to what is often seen in Byzantine consensus problems but there are subtle differences and relaxations.
Firstly, the agreement property only holds if honest nodes do not output \emph{unknown}.
For example, it is ok if two honest nodes output \emph{valid} and \emph{unknown}, but it is not ok to output \emph{valid} and \emph{invalid}.
Secondly, the validity is a relaxation of what is typically seen in Byzantine consensus problems,
namely we do not make any guarantee on whether the transaction is \emph{valid} even if all nodes are honest,
only that it is correct according to the $\textsf{get\_validity}(\cdot)$ defined by the protocol.

Our problem is purposefully made to be application neutural,
i.e. there are no constraints on the semantics of transaction.
This is so that the protocol can act as a backbone to many applications.
Due to this fact, we also do not consider global fork prevention or detection,
as some application may not need such strong guarantees such as recording the number of bytes uploaded and downloaded in Tribler~\cite{pimotte, pouwelse2008tribler}.
On the other hand, we give an alternative construction that does have fork detection in~\Cref{sec:fork}.

>>>>

Note that the agreement and validity property are similar to what is often seen in Byzantine consensus problems but there are subtle differences and relaxations.
Firstly, the agreement property only holds if honest nodes do not output \emph{unknown}.
For example, it is OK if two honest nodes output \emph{valid} and \emph{unknown}, but it is not OK to output \emph{valid} and \emph{invalid}.
Secondly, the validity is a relaxation of what is typically seen in Byzantine consensus problems,
namely we do not make any guarantee on whether the transaction is \emph{valid} even if all nodes are honest,
only that it is correct according to the $\textsf{get\_validity}(\cdot)$ defined by the protocol.

Our problem is purposefully made to be application neutral,
i.e. there are no constraints on the semantics of transaction.
This is so that the protocol can act as a backbone to many applications.
Due to this fact, we also do not consider global fork prevention or detection,
as some application may not need such strong guarantees such as recording the number of bytes uploaded and downloaded in Tribler~\cite{pimotte, pouwelse2008tribler}.
On the other hand, we give an alternative construction that does have fork detection in~\Cref{sec:fork}.

### 2017-08-13 paper/s3-system.tex
Spell check paper

$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ and each CP in $\C_r$ belong to a different node\footnote{
                $\C_r$ is a tuple but we abuse the notation here by writing $|\C_r|$ to mean the number of CP blocks in the second element of $\C_r$.}.
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
\end{enumerate}
\end{definition}
These properties are similar to Byzantine consensus properties but there are subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds,
because a failure in one round will lead to failures in sebsequent rounds.

@@

Continuing, when $\F_{r}$ reaches agreement on $\C_{r+1}$,
they immediately broadcast\footnote{An alternative to using broadcasting is to use an epidemic protocl~\cite{eugster2004epidemic}, 
as long as it can guarantee delivery.} two messages to all the nodes---
first the consensus message $\langle \texttt{cons\_msg}, \C_{r+1} \rangle$,
and second the signature message $\langle \texttt{cons\_sig}, r, sig \rangle$.
The reason for sending \texttt{cons\_sig} is the following.
Recall that channels are not authenticated, 
and there are no signatures in $\C_{r + 1}$.
If a non-facilitator sees some $\C_{r + 1}$, it cannot immediately trust it because it may have been forged.
Thus, To guarantee authenticity, every facilitator sends an additional message that is the signature of $\C_{r + 1}$.

@@

The TX protocol, shown in \Cref{alg:tx-proto}, is run by all nodes.
It is also known as True Halves, first described informally by Veldhuisen~\cite[Chapter~3.2]{truehalves}.
Nodes that wish to initiate a transaction calls $\textsf{new\_tx}(pk_v, m, txid)$ (\Cref{alg:new-tx}) with the intended counterparty $v$ identified by $pk_v$ and message $m$.
$txid$ should be a uniformly distributed random value, i.e. $txid \in_R \{0, 1\}^{256}$,
then sends $\langle \texttt{tx\_req}, t_{u, h}\rangle$ to $v$.

@@

We offer two approaches to do total fork detection.
First and the easiest solution is to simply ask for the complete chain of the counterparty.
The verifier can be sure that there are no forks if the following holds.
\begin{enumerate}
    \item The hash pointers are correct.
    \item All the CP blocks are in consensus.
    \item The TX of interest is in the chian.
\end{enumerate}
We use this approach in our prior work on Implicit Consensus~\cite{implicitconsensus}.
Nodes employ caching to minimise communication costs, we call this effect spontaneous sharding.

>>>>

$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ and each CP in $\C_r$ belong to a different node\footnote{
                $\C_r$ is a tuple but we abuse the notation here by writing $|\C_r|$ to mean the number of CP blocks in the second element of $\C_r$.}.
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
\end{enumerate}
\end{definition}
These properties are similar to Byzantine consensus properties but there are subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds,
because a failure in one round will lead to failures in subsequent rounds.

@@

Continuing, when $\F_{r}$ reaches agreement on $\C_{r+1}$,
they immediately broadcast\footnote{An alternative to using broadcasting is to use an epidemic protocol~\cite{eugster2004epidemic}, 
as long as it can guarantee delivery.} two messages to all the nodes---
first the consensus message $\langle \texttt{cons\_msg}, \C_{r+1} \rangle$,
and second the signature message $\langle \texttt{cons\_sig}, r, sig \rangle$.
The reason for sending \texttt{cons\_sig} is the following.
Recall that channels are not authenticated, 
and there are no signatures in $\C_{r + 1}$.
If a non-facilitator sees some $\C_{r + 1}$, it cannot immediately trust it because it may have been forged.
Thus, To guarantee authenticity, every facilitator sends an additional message that is the signature of $\C_{r + 1}$.

@@

The TX protocol, shown in \Cref{alg:tx-proto}, is run by all nodes.
It is also known as True Halves, first described informally by Veldhuisen~\cite[Chapter~3.2]{truehalves}.
Nodes that wish to initiate a transaction calls $\textsf{new\_tx}(pk_v, m, txid)$ (\Cref{alg:new-tx}) with the intended counterparty $v$ identified by $pk_v$ and message $m$.
$txid$ should be a uniformly distributed random value, i.e. $txid \in_R \{0, 1\}^{256}$.
Then the initiator sends $\langle \texttt{tx\_req}, t_{u, h}\rangle$ to $v$.

@@

We offer two approaches to do total fork detection.
First and the easiest solution is to simply ask for the complete chain of the counterparty.
The verifier can be sure that there are no forks if the following holds.
\begin{enumerate}
    \item The hash pointers are correct.
    \item All the CP blocks are in consensus.
    \item The TX of interest is in the chain.
\end{enumerate}
We use this approach in our prior work on Implicit Consensus~\cite{implicitconsensus}.
Nodes employ caching to minimise communication costs, we call this effect spontaneous sharding.

### 2017-08-13 paper/s4-analysis.tex
Spell check paper

\section{Correctness and fault tolerance analysis}
\label{sec:analysis}
We evaluate our system analytically to ensure the desired properties (\Cref{def:consensus} and \Cref{def:validation}) hold.
An informal argument is given in this section, we refer to~\cite[Chapter 4]{checo}??? for an indepth analysis.

@@

Fairnress holds if we model $\textsf{H}(\cdot)$ as a query to the random oracle.
Sorting nodes by the luck value $\textsf{H}(\C || pk)$ can be seen as a random permutation of a list of nodes.
Therefore every node has the same probability of becoming a facilitator.

@@

The validty property holds because we use $\textsf{get\_validity}(\cdot)$ in the validation protocol.
The agreement property holds because we model $\textsf{H}(\cdot)$ as a query to a random oracle.
Suppose two honest nodes decided on two different state, \emph{valid} and \emph{invalid} for the same transaction.
Due to the properties of the consensus protocol, the agreed enclosure for the transaction must be the same.
For that to happen, two agreed fragments must exist for the same transaction.
Recall that blocks form a hash chain.
So this cannot happen unless the adversary can compute the inverse of $\textsf{H}(\cdot)$ with high probability.

@@

\subsection{Fault tolerance}
Finally, we consider the effect when the number of adversaries is more than $t$.
This is useful because in practice it is difficult to guarantee that $t$ satisfies $n \ge 3t + 1$,
especially when $N$ is large.
Hence we are interested in the probability for this to happen under our facilitator election process.
The problem is modeled by a hypergeometric distribution,
where the random variable $X$ is the number of malicious nodes.
For our system to fail, we are interested in the following probability.
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1]
$$
Let $E[X] = n\alpha$ where $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor/n < (\lfloor  \frac{n - 1}{3} \rfloor + 1) / n$.
Using the tail inequality found in~\cite{skala2013hypergeometric}
$$
\Pr[X \ge E[X] + \tau n] \le e^{-2\tau^2n},
$$
and setting 
$$
\tau = \frac{\lfloor \frac{n-1}{3} \rfloor + 1}{n} - \alpha,
$$
we arrive at the following bound
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1] \le e^{-2 \big(\frac{\lfloor  \frac{n - 1}{3} \rfloor + 1}{n} - \alpha \big)^2 n}.
$$

>>>>

\section{Correctness and fault tolerance analysis}
\label{sec:analysis}
We evaluate our system analytically to ensure the desired properties (\Cref{def:consensus} and \Cref{def:validation}) hold.
An informal argument is given in this section, we refer to~\cite[Chapter 4]{checo}??? for an in-depth analysis.

@@

Fairness holds if we model $\textsf{H}(\cdot)$ as a query to the random oracle.
Sorting nodes by the luck value $\textsf{H}(\C || pk)$ can be seen as a random permutation of a list of nodes.
Therefore every node has the same probability of becoming a facilitator.

@@

The validity property holds because we use $\textsf{get\_validity}(\cdot)$ in the validation protocol.
The agreement property holds because we model $\textsf{H}(\cdot)$ as a query to a random oracle.
Suppose two honest nodes decided on two different state, \emph{valid} and \emph{invalid} for the same transaction.
Due to the properties of the consensus protocol, the agreed enclosure for the transaction must be the same.
For that to happen, two agreed fragments must exist for the same transaction.
Recall that blocks form a hash chain.
So this cannot happen unless the adversary can compute the inverse of $\textsf{H}(\cdot)$ with high probability.

@@

\subsection{Fault tolerance}
Finally, we consider the effect when the number of adversaries is more than $t$.
This is useful because in practice it is difficult to guarantee that $t$ satisfies $n \ge 3t + 1$,
especially when $N$ is large.
Hence we are interested in the probability for this to happen under our facilitator election process.
The problem is modelled by a hypergeometric distribution,
where the random variable $X$ is the number of malicious nodes.
For our system to fail, we are interested in the following probability.
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1]
$$
Let $E[X] = n\alpha$ where $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor/n < (\lfloor  \frac{n - 1}{3} \rfloor + 1) / n$.
Using the tail inequality found in~\cite{skala2013hypergeometric}
$$
\Pr[X \ge E[X] + \tau n] \le e^{-2\tau^2n},
$$
and setting 
$$
\tau = \frac{\lfloor \frac{n-1}{3} \rfloor + 1}{n} - \alpha,
$$
we arrive at the following bound
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1] \le e^{-2 \big(\frac{\lfloor  \frac{n - 1}{3} \rfloor + 1}{n} - \alpha \big)^2 n}.
$$
